Fully Automatic Loop-free Program Synthesis by Bounded Model Checking

### 2013-10-09 paper/paper.tex
Added parameter searching

@@

\begin{figure}
\begin{tikzpicture}{node distance=2cm, auto}
\tikzstyle{decision} = [diamond, draw, fill=blue!20, 
    text width=4.5em, text badly centered, node distance=3cm, inner sep=0pt]
\tikzstyle{block} = [rectangle, draw, fill=blue!20, 
    text width=5em, text centered, rounded corners, minimum height=4em]
\tikzstyle{line} = [draw, -latex']
\tikzstyle{cloud} = [draw, ellipse,fill=red!20, node distance=3cm,
    minimum height=2em]

@@

 \node [decision, below of=synthsucc, node distance=2.5cm] (verif) {{\sc Verif} succeeds?};
 \node [decision, right of=verif] (ck) {$c < k$?};

@@

 \node [block, below of=ck, node distance=2.5cm] (incc) {$c := c+1$};
 \node [block, right of=incc, node distance=2cm] (inck) {$c := 0$\\ $k := k+1$};

 \node [block, below of=verifw, node distance=2.5cm] (incw) {$w := w+1$};
 \node [block, left of=incw, node distance=2cm] (iterate) {Loop to {\sc synth}};

@@

 \path [line] (ck) -- node [left] {Yes} (incc);
 \path [line] (ck) -| node  [above, near start]  {No}(inck);

 \path [line] (verifw) -- node [right] {Yes} (incw);
 \path [line] (verifw) -| node [above, near start] {No} (iterate);
\end{tikzpicture}

>>>>

Sometimes a program will be correct for some particular word width $w$, but is
not correct for $w' > w$ even if the constants are replaced with appropriate ones.
When this happens we are forced to increase $w$ and continue synthesising.

@@

\subsection{Searching the Program Space}
The key to our automation approach is to come up with a sensible way in which to
adjust the $\mathcal{L}$-parameters in order to cover all possible programs.
After each round of {\sc synth}, we may need to adjust the parameters.  The
logic for these adjustments is shown as a tree in Fig~\ref{fig:paramsflow}.

\begin{figure}
\begin{tikzpicture}[scale=0.9, transform shape, node distance=2cm, auto]
\tikzstyle{decision} = [diamond, draw, fill=blue!20, 
    text width=4.5em, text badly centered, node distance=3cm, inner sep=0pt]
\tikzstyle{block} = [rectangle, draw, fill=blue!20, 
    text width=5em, text centered, rounded corners, minimum height=4em]
\tikzstyle{line} = [draw, -latex']
\tikzstyle{cloud} = [draw, ellipse,fill=red!20, node distance=3cm,
    minimum height=2em]

@@

 \node [decision, below of=synthsucc, node distance=2.5cm] (verif) {{\sc Verif} succeeds?};
 \node [decision, right of=verif] (ck) {$c < l$?};

@@

 \node [block, below of=ck, node distance=2.5cm] (incc) {$c := c+1$};
 \node [block, right of=incc, node distance=2cm] (incl) {$c := 0$\\ $l := l+1$};

 \node [decision, below of=verifw, node distance=3cm] (gen) {Extend succeeds?};
 \node [block, left of=gen, node distance=2.5cm] (iterate) {Loop to {\sc synth}};

 \node [block, below of=gen, node distance=2.5cm] (incw) {$w := w+1$};

@@

 \path [line] (ck) -- node [left] {Yes} (incc);
 \path [line] (ck) -| node  [above, near start]  {No} (incl);

 \path [line] (verifw) -- node [right] {Yes} (gen);
 \path [line] (verifw) -| node [above] {No} (iterate);

 \path [line] (gen) -| node [below, near start] {Yes} (done);
 \path [line] (gen) -- node [right] {No} (incw);

 \path [dotted, line] (iterate.west) |- (synthsucc);
\end{tikzpicture}
